---
title: "Gov 50 Final Project"
author: Zophia Cherrier
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

I am interested in exploring data related to U.S. public opinions on climate change and how they have changed over time. I also hope to find a data set that takes into account how political party affiliation impacts opinions on climate change, and further, the degree of action that should be taken in addressing this existential crisis.  

## Proposal
 
Do the majority of adult Americans believe that the United States government should be doing more to reduce the effects of global climate change? In this study, I plan to examine the extent to which the American public believes the U.S. is taking meaningful steps to combat climate change. I also plan to observe differences of opinions of adults within the Republican versus Democratic parties on whether the government should be doing more to reduce the effects of climate change. I hypothesize that a majority of Americans believe that the federal government should be doing more to protect the environment by reducing the effects of global warming. I make this hypothesis because public concern over climate change has been steadily rising in recent years, especially among members of the Democratic Party. Additionally, environmental activism seems to be a very important issue especially for those of younger generations in the current social landscape. Furthermore, I hypothesize that a greater percentage of Democrats believe that the federal government is not doing enough to protect the environment by reducing the effects of climate change than Republicans, due to the fact that the Democrats have made climate change a center issue in their party platform while Republicans have not made the environment a party priority and support the fossil fuel industry. My sample is comprised of 5,162 adults in the U.S. who are of voting age from American National Election Survey data from the Gov50 data package. The explanatory variable of interest is political affiliation and whether the individual being surveyed is affiliated with the Democratic or Republican Party. The variable of political party affiliation is coded on a 1-7 scale, where 1 indicates a strong Democrat while 7 indicates a strong Republican. The outcome variable is whether the individual believes the federal government is taking proper measures to reduce the effects of climate change or should be doing more. The outcome variable is coded 1 if the respondent thinks the government should be doing more about climate change and 0 if the government is doing enough. If I observe that a greater percentage of Democrats believe that the government should be doing more (1) to reduce the impacts of global warming than Republicans, this would support my hypothesis. However, if I observe that a greater percentage of Republicans believe that the government is doing too little (0) to reduce the effects of climate change, this would provide evidence against my hypothesis. 

## Milestone #3

```{r}
library(gov50data)
library(ggplot2)
library(dplyr)
library(infer)
library(tidyverse)
anes <- anes
anes
##
anes |>
  group_by(envir_doing_more) |>
  summarize(n = n()) |>
  mutate(prop = n / sum(n)) |>
  ggplot(data = anes, 
         mapping = aes(x = envir_doing_more)) +
  geom_bar() +
  labs(title = "American Opinion on Government Action on Climate Change")

anes_party <- anes |>
  group_by(pid7) |>
  summarize(envir_doing_more_mean = mean(envir_doing_more))
anes_party

anes_party_bar <- anes_party |>
  ggplot(mapping = aes(x = pid7, y = envir_doing_more_mean)) +
  geom_col() +
  labs(x = "Party Identification 1 (Strong Democrat) to 7 (Strong Republican)", title = "American Opinion on Government Action on Climate Change With Respect to Party Identification")
anes_party_bar


```
## Milestone #4

```{r}
anes_party_table <- anes |>
  group_by(pid7) |>
  summarize(envir_doing_more_mean = mean(envir_doing_more)) 
anes_party_table

knitr::kable(anes_party_table, col.names = c("Party ID", "envir_doing_more_mean"))


```

From the first table in my research, "American Opinion on Government Action on Climate Change" one can observe that the majority of Americans believe the government should be doing more to combat climate change, as around 2000 respondents said the government was doing enough while around 3000 said the government should take more action on the issue. Therefore, based on this sample, a roughly 60 percent majority of Americans would believe that the government should be doing more to curtail global warming, supporting my hypothesis that most Americans feel that the government should be doing more. I also hypothesized that a greater percentage of Democrats believe that the federal government is not doing enough to protect the environment by reducing the effects of climate change than Republicans, where my second visualization, "American Opinion on Government Action on Climate Change with Respect to Party Identification" demonstrates this. The means of those who believe the government should be doing more are significantly higher for those who identify as Democrats or strong Democrats (1- .93 2- .87, 3- .94), than those who identify as Republicans or strong Republicans (5- .32, 6- .40, 7- .13), as more than half the Democrats in PIDs 1, 2, and 3 believe the government should being doing more. What I also found interesting in the table means was that for those down the middle of party identification in party ID 4, the mean of those who believe the government should be taking more action on climate change was .62, proving that more than half the moderates also believe that more government intervention is needed. Overall, the trends of means that the government should be doing more generally decreased as ideology shifted towards Republican and PID increased on the 7 point scale. The only notable exceptions were that on both the Democratic and Republican sides, PID 5's envir_doing_more_mean (.32) was less than PID 6's envir_doing_more_mean (.40) even though they identified less strongly as a Republican, while PID 2's mean of .87 was less than PID 3's mean of .93 even though PID 2 identified more strongly as Democrats.




