---
title: "Gov 50 Final Project"
author: Zophia Cherrier
description: "U.S. Public Opinion on Climate Change"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

  I am interested in exploring data related to U.S. public opinions on climate change. I also hope to find a data set that takes into account how political party affiliation impacts opinions on climate change, and further, the degree of action that should be taken in addressing this existential crisis.  

## Introduction
 
  Do the majority of adult Americans believe that the United States government should be doing more to reduce the effects of global climate change? In this study, I plan to examine the extent to which the American public believes the U.S. is taking meaningful steps to combat climate change. I also plan to observe differences of opinion between adults within the Republican versus Democratic parties on whether the government should be doing more to reduce the effects of climate change. I hypothesize that a majority of Americans believe that the federal government should be doing more to protect the environment by reducing the effects of global warming. I make this hypothesis because public concern over climate change has been steadily rising in recent years, especially among members of the Democratic Party. Additionally, environmental activism seems to be a very important issue, especially for those of younger generations in the current social landscape. Furthermore, I hypothesize that a greater percentage of Democrats believe that the federal government is not doing enough to protect the environment by reducing the effects of climate change than Republicans, due to the fact that the Democrats have made climate change a central issue in their party platform while Republicans have not made the environment a party priority and support the fossil fuel industry. I also examine whether party identification has a causal effect on opinion on climate change action. 

## The Data 

  My sample is comprised of 5,162 adults in the U.S. who are of voting age from American National Election Survey data from the Gov50 data package. The data was gathered in a cross-sectional study, as it is observational in nature and descriptive research where no treatment was applied. The researchers simply recorded information on the individual’s party ID and opinion on climate action at a specific point in time and did not manipulate any variables, just observing and recording what was present in the world. Because this study was descriptive and observational, only correlation and not causation can be concluded. 
  The explanatory variable of interest is political affiliation and whether the individual being surveyed is affiliated with the Democratic or Republican Party. The variable of political party affiliation is coded on a 1-7 scale, where 1 indicates a strong Democrat while 7 indicates a strong Republican. The outcome variable is whether the individual believes the federal government is taking proper measures to reduce the effects of climate change or should be doing more. The outcome variable is coded 1 if the respondent thinks the government should be doing more about climate change and 0 if the government is doing enough. If I observe that a greater percentage of Democrats believe that the government should be doing more (1) to reduce the impacts of global warming than Republicans, this would support my hypothesis. However, if I observe that a greater percentage of Republicans believe that the government is doing too little (0) to reduce the effects of climate change, this would provide evidence against my hypothesis.


## Visualizations

```{r}
library(gov50data)
library(ggplot2)
library(dplyr)
library(infer)
library(tidyverse)
anes <- anes 
anes
##
anes |>
  group_by(envir_doing_more) |>
  summarize(n = n()) |>
  mutate(prop = n / sum(n)) |>
  ggplot(data = anes, 
         mapping = aes(x = envir_doing_more)) +
  geom_bar(aes(x = envir_doing_more, fill = "red")) +
  labs(title = "American Opinion on Government Action on Climate Change", fill = "Count")

anes_party <- anes |>
  group_by(pid7) |>
  summarize(envir_doing_more_mean = mean(envir_doing_more))
anes_party

anes_party_bar <- anes_party |>
  ggplot(mapping = aes(fill = envir_doing_more_mean, x = pid7, y = envir_doing_more_mean)) +
  geom_bar(stat = "identity") + scale_fill_gradient(low = "red", high = "blue") +
  labs(fill = "Climate Change Opinion Proportion", x = "Party Identification 1 (Strong Democrat) to 7 (Strong Republican)", title = "American Opinion on Government Action on Climate Change With Respect to Party Identification")
anes_party_bar


```
## Results Summary

```{r}
anes_party_table <- anes |>
  group_by(pid7) |>
  summarize(envir_doing_more_mean = mean(envir_doing_more)) 
anes_party_table

knitr::kable(anes_party_table, col.names = c("Party ID", "envir_doing_more_mean"))


```

## Visualization Results Explained

  From the first table in my research, "American Opinion on Government Action on Climate Change" one can observe that the majority of Americans believe the government should be doing more to combat climate change, as around 2000 respondents said the government was doing enough while around 3000 said the government should take more action on the issue. Therefore, based on this sample, a roughly 60 percent majority of Americans would believe that the government should be doing more to curtail global warming, supporting my hypothesis that most Americans feel that the government should be doing more. I also hypothesized that a greater percentage of Democrats believe that the federal government is not doing enough to protect the environment by reducing the effects of climate change than Republicans, where my second visualization, "American Opinion on Government Action on Climate Change with Respect to Party Identification" demonstrates this. The means of those who believe the government should be doing more are significantly higher for those who identify as Democrats or strong Democrats (1- .93 2- .87, 3- .94), than those who identify as Republicans or strong Republicans (5- .32, 6- .40, 7- .13), as more than half the Democrats in PIDs 1, 2, and 3 believe the government should be doing more. What I also found interesting in the table means was that for those down the middle of party identification in party ID 4, the mean of those who believe the government should be taking more action on climate change was .62, proving that more than half the moderates also believe that more government intervention is needed. Overall, the trends of means that the government should be doing more generally decreased as ideology shifted towards Republican and PID increased on the 7-point scale. The only notable exceptions were that on both the Democratic and Republican sides, PID 5's envir_doing_more_mean (.32) was less than PID 6's envir_doing_more_mean (.40) even though they identified less strongly as a Republican, while PID 2's mean of .87 was less than PID 3's mean of .93 even though PID 2 identified more strongly as Democrats.


## Regression and Multiple Regression

```{r}
fit <- lm(envir_doing_more ~ pid7, data = anes)
fit

fit.mult <- lm(envir_doing_more ~ pid7 + state, data = anes)
fit.mult
```
```{r}
library(broom)
library(tidyverse)
anes.multreg <- lm(envir_doing_more ~ pid7 + state, data = anes)
anes.multreg
tidy(anes.multreg) |>
  knitr::kable(digits = 3)

anes.reg <- lm(envir_doing_more ~ pid7, data = anes)
anes.reg
tidy(anes.reg) |>
  knitr::kable(digits = 3)
```

## Regression Results Explained

  As far as the first linear regression between PID and climate change opinion, the correlation coefficient could be interpreted as when PID increases by 1 point, climate change opinion decreases by 0.1382 percentage points, showing a negative correlation between PID and opinions that the government should be doing more to combat climate change. The multiple regression took into account not only PID but the possible confounder of the state where the individual was from since many specific states rely on fossil fuel industries and might be economically opposed to a green transition. The correlation coefficient for PID could be interpreted as when PID increases by one point, climate change opinion decreases by 0.135944 when holding the state variable constant, once again showing a negative correlation between PID and opinions that the government should be doing more to combat climate change. Although, this correlation was slightly less great in magnitude (0.135944) than the simple regression (0.1382). As far as statistical significance, it is determined that the alpha level is 0.05 and the null hypothesis is that there is no relationship between PID and climate change opinion. The p-value for the first single variable regression was zero which was less than 0.05, so there is strong evidence to reject the null hypothesis that there is no relationship between PID and opinion on climate change measures. The p-value for the multiple regression was also zero and less than 0.05, so there is once again strong evidence to reject the null hypothesis that there is no relationship between PID and opinion on climate change action, even when controlling for confounders like state residency. Therefore, there is decent evidence to conclude that there is a statistically significant negative linear relationship between PID and opinion on climate change because the correlation coefficient is significantly different from zero. However, this coefficient does not represent a certain causal effect between PID and opinion on climate action since this study was descriptive and observational rather than experimental where treatment and control were applied. 
  
## Conclusion

  Ultimately, the data from this ANES survey demonstrates how the majority of Americans believe the government should be doing more to combat climate change and a greater percentage of Democrats believe that the federal government is not doing enough to protect the environment by reducing the effects of climate change than Republicans. Both the single and multiple linear regressions displayed a negative correlation between PID and opinions that the government should be doing more to combat climate change. In the first linear regression, when PID increases by 1 point, climate change opinion decreases by 0.1382 while in the multiple regression, when PID increases by one point, climate change opinion decreases by 0.135944 when holding the state variable constant. The p-values for both of these regressions substantiated claims that the correlations were statistically significant since the p-values of 0 were lower than the alpha threshold of 0.05. Although, causation cannot be concluded with certainty since this was a cross-sectional study and not an experiment and other possible confounders were not recorded in the data. The limitation of this study was that the variables of gender and race were also not recorded in the data. These demographics could also serve as possible confounders that could influence opinions on climate change other than simply party identification. For instance, many studies show relationships where women tend to be more sympathetic to the cause of climate change while certain races are disproportionately affected by pollution and contamination, influencing opinion. Overall, the study could be improved in the future by including data on these variables and running another multiple linear regression between PID, gender, race, and state and opinion on government action on climate change to control for more confounding variables that could also affect opinion results. It would also be helpful to observe how these patterns have changed over time instead of a year snapshot and how that public opinion translates into political support for green energy policies. 






